fl0w 2.0 - a development environment for the\\ KIPR Wallaby

### 2017-03-12 paper.tex
Improved: undergr0und.js, behem0th, fl0w server

The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A. Melnikov} in arraybuffer mode. Only the Python version can be started in server mode because It was created to mitigate the problems fl0ws explorative development style created. Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols. This was done because all monolithic designs became too inconsistent. undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.

\subsubsection{undergr0und.js}
undergr0und.js is the feature complete client-side JavaScript port of undergr0und. It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server. It is based on the Python version but does not implement the server because there is currently no need for that functionality.

@@

\subsection{behem0th}
behem0th is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment. It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und. It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A. Melnikov} because the in-browser components of fl0w never interact with it. File system events are detected with watchdog

\subsubsection{Synchronization}
Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server.

@@

\subsubsection{Metadata}
Metadata

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain information from them. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for DOM manipulation.

@@

\subsection{edit0r}
edit0r is the Sublime Text 3 plugin. It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in line sensor readouts. It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static. behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.

@@

\subsubsection{Wallaby}

@@

>>>>

The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A. Melnikov} in arraybuffer mode. It was created to mitigate the problems fl0ws explorative development style created. Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols. This was done because all monolithic designs became too inconsistent over time. undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.

\subsubsection{undergr0und.js}
undergr0und.js is the feature complete client-side JavaScript port of undergr0und that was required for dashb0ard, the browser-based front-end for fl0w. It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server. It is based on the Python version but does not implement the server because there is currently no need for that functionality. undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A. Melnikov}. browserify\cite{browserify:James Halliday} is used to create the browser version.

@@

\subsection{behem0th}
behem0th is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment. It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und. It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A. Melnikov} because the in-browser components of fl0w never interact with it. File system events are detected with watchdog\cite{watchdog:Yesudeep Mangalapilly}.

\subsubsection{Synchronization}
Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server. Synchronization with a theoretically indefinite amount of clients is possible.

@@

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain sensor readouts as well as debug logs. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.

@@

\subsection{edit0r}
edit0r is the Sublime Text 3 plugin. It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in-line sensor readouts. It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static. behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.

@@

\subsubsection{Wallaby client}

\subsubsection{Server}
The server keeps track of all clients and provides means to acquire their peer IDs, which are used by undergr0und to target specific clients. Additionally it serves dashb0ard and handles program compilation. It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network. In that case the start is interrupted and the Wallaby client connects to the available server instance, otherwise server and client are started.

@@

\bibitem{browserify:James Halliday}
James Halliday, \emph{browserify}, \url{http://browserify.org/},\\ product page,
accessed February 9th 2017

\bibitem{Node.js:Node.js Foundation}
Node.js Foundation, \emph{Node.js}, \url{https://nodejs.org},\\ product page,
accessed February 9th 2017

\bibitem{watchdog:Yesudeep Mangalapilly}
Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog}, \\ source code, accessed February 9th 2017
